Supplements for the manuscript `Variation in gaze following across the life span: A process-level perspective'

### 2024-04-19 paper/manuscript.Rmd
anonymize supplements, correct small mistakes

(ref:figlab1) **Developmental trajectory of gaze following across the lifespan**. Grey dots show the mean level of imprecision (ie., absolute distance between the target's center and the participant's click) for each subject averaged across trials. The unit of imprecision is counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. Blue lines show 100 draws from the expectation of the posterior predictive distribution of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line. Vertical, black, dashed lines show the locations of the changes with the highest posterior probability according to our Bayesian change point analysis.

@@

High levels of variation pointed to substantial individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]). We found substantial evidence for a non-linear development in gaze following across the lifespan. The Gaussian process model was clearly preferred over the polynomial models due to the highest predictive accuracy according to the LOO ELPD estimates: elpd_diff between Gaussian process and cubic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mcubic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mcubic"]`); elpd_diff between Gaussian process and quadratic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mquadratic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mquadratic"]`); elpd_diff between Gaussian process and linear model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mlinear"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mlinear"]`); all in favor of the Gaussian process model. Moreover, the Gaussian Process model showed the greatest model weight (approximating `r lifespan_mcomparison$modelweight[lifespan_mcomparison$model == "mgaussianprocess"]`). For the imprecision in gaze following, the standard deviation of the Gaussian process (SD = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) indicated nonlinearity.

@@

(ref:figlab3) **Gaze model** (A) Developmental trajectory of the estimated model parameter. Grey dots show individual level parameter values. The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it. The large black point with 95% HDI shows the mean of the model parameter for the adult sample. We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting. (B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group. In the child sample, color denotes age in years. Grey regression lines with 95% CI show smooth conditional means based on linear models, with *Pearson*'s correlation coefficient *r*. (C) Pattern recovery. Imprecision in target width for each target bin by age group. Model predictions in blue; data in grey. (D) Correlation between the observed data and the predictions of the three models by target position and age group (across individuals; only for the child sample).

>>>>

(ref:figlab1) **Developmental trajectory of gaze following across the lifespan**. Grey dots show the mean level of imprecision (i.e., absolute distance between the target's center and the participant's click) for each subject averaged across trials. The unit of imprecision is counted in target width, i.e., a participant with imprecision of 1 clicked on average one target width to the left or right of the true target center. Blue lines show 100 draws from the expectation of the posterior predictive distribution of the Gaussian Process model, with its mean predicted developmental trajectory as a solid black line. Vertical, black, dashed lines show the locations of the changes with the highest posterior probability according to our Bayesian change point analysis.

@@

High levels of variation pointed to substantial individual differences in all age groups (overall imprecision mean = `r lifespan_variation$imprecision_mean`, sd = `r lifespan_variation$imprecision_sd`, range = [`r lifespan_variation$imprecision_min` - `r lifespan_variation$imprecision_max`]). We found substantial evidence for a non-linear development in gaze following across the lifespan (see Figure \@ref(fig:fig1)). The Gaussian process model was clearly preferred over the polynomial models due to the highest predictive accuracy according to the LOO ELPD estimates: elpd_diff between Gaussian process and cubic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mcubic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mcubic"]`); elpd_diff between Gaussian process and quadratic model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mquadratic"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mquadratic"]`); elpd_diff between Gaussian process and linear model = `r lifespan_mcomparison$elpd_diff[lifespan_mcomparison$model == "mlinear"]` (SE = `r lifespan_mcomparison$se_diff[lifespan_mcomparison$model == "mlinear"]`); all in favor of the Gaussian process model. Moreover, the Gaussian Process model showed the greatest model weight (approximating `r lifespan_mcomparison$modelweight[lifespan_mcomparison$model == "mgaussianprocess"]`). For the imprecision in gaze following, the standard deviation of the Gaussian process (SD = `r lifespan_gp$estimate[lifespan_gp$param == "sdgp(gpage_centered)"]`, 95% CrI [`r lifespan_gp$l_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`; `r lifespan_gp$u_95_percent_ci[lifespan_gp$param == "sdgp(gpage_centered)"]`]) indicated nonlinearity.

@@

(ref:figlab3) **Gaze model results** (A) Developmental trajectory of the estimated model parameter. Grey dots show individual level parameter values. The black line shows the maximum a posteriori (MAP) estimate; blue lines show 1000 draws from it. The large black point with 95% HDI shows the mean of the model parameter for the adult sample. We added minimal horizontal and vertical noise to the adult individual level parameter values to avoid overplotting. (B) Correlation between estimated mode of the model parameter and data mean per individual, faceted by age group. In the child sample, color denotes age in years. Grey regression lines with 95% CI show smooth conditional means based on linear models, with *Pearson*'s correlation coefficient *r*. (C) Pattern recovery. Imprecision in target width for each target bin by age group. Model predictions in blue; data in grey. (D) Correlation between the observed data and the predictions of the three models by target position and age group (across individuals; only for the child sample).

### 2024-04-19 supplements/supplements.Rmd
anonymize supplements, correct small mistakes

---
title             : "Supplements for the manuscript  'Variation in gaze following across the life span: A process-level perspective'"
shorttitle        : "Supplements"
author:

  - name          : "Julia Prein"
    affiliation   : "1,2"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "1"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1,*"
  - name          : "Manuel Bohn"
    affiliation   : "1,2,*"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
  - id            : "*"
    institution   : "shared last authorship"  
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa7"
classoption       : "man"
output            : papaja::apa6_pdf
header-includes:
  - \usepackage{setspace}
  - \usepackage{float}
  - \captionsetup[figure]{font={stretch=1}}
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# Study 1: Lifespan
## Participants
```{r lifespan_sample, include = T, out.width = "100%"}
lifespan_sample <- readRDS("../saves/lifespan_sample.rds")

knitr::kable(lifespan_table, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

@@

Originally, we fitted the models on a trial-by-trial basis with the following structure in `R: performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`. However, the Gaussian Process model was computationally heavy. Therefore, we simplified the model structure, aggregated data on a subject level, and included only age as an effect. We then visually compared the model predictions of the original and the simplified models with each other. As you can see in Figure \@ref(fig:fig1), results of the two models did not differ notably.

(ref:figlab1) **Comparison between models on a trial- or subject-level**. Grey dots show data of each trial. Solid lines show the mean predicted developmental trajectory for both models. Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level). 
```{r fig1, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab1)"}
knitr::include_graphics("../figures/supplements_lifespan_modelstructure.pdf")
```

@@

# Study 2: Computational cognitive model 
## Analysis
### Gaze model prediction
Our gaze model predicts that TANGO trials vary in their difficulty, resulting in a U-shaped pattern: Participants' imprecision should increase, the further out the target lands (towards the very left/right sides). Since the task is presented on a screen, there is a natural border towards one side. Imagine the target lands to the very right side. Participants' imprecision cannot click further right because the screen ends; all their uncertainty about the target location faces the inner, left-hand side now. Therefore, the predicted U-shaped pattern should decrease again towards the screen borders. For previous reliability analyses [@prein2023tango], we had increased the trial number for an adult sample (N = 70; each 30 trials). Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \@ref(fig:fig2)).

(ref:figlab2) **Gaze funnel for adult sample with higher trial number**.
```{r fig2, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab2)"}
knitr::include_graphics("../figures/gazefunnel_adults.pdf")
```

## Inference parameter estimates per individual
As can be seen in Figure \@ref(fig:fig3) and Figure \@ref(fig:fig4), the gaze model estimated the inference parameter for each individual. Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty. In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.

(ref:figlab3) **Gaze model estimates faceted by individual**.
```{r fig3, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab3)"}
knitr::include_graphics("../figures/supplements_gazemodel_facetedinference.pdf")
```

(ref:figlab4) **Gaze model estimates ordered by descending inference parameter value**.
```{r fig4, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab4)"}
knitr::include_graphics("../figures/supplements_gazemodel_indinference.pdf")
```

@@

Please note that our random guessing model acts like 100% noise: the predictions of a participant’s click on a trial level range uniformly from 0 to 1920 (the whole screen range). The mean comes down to the center, namely 960. However, as you can see in the figure below, the U shape is weaker compared to the other models (Figure 1A). Most importantly, note that this is only the case when you average across all the trials. When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure 5C). In our correlational plots (Figure 5B), we see that the gaze model is clearly favored. This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.

(ref:figlab5) **Predictions of alternative models across target positions.** A: Predicted U-pattern across target positions by the different models. Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click. B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group. C: Predicted click coordinates (cf. not imprecision) by target position across the different models.

```{r fig5, include = T, out.width = "100%", fig.align = "center", fig.cap = "(ref:figlab5)"}
knitr::include_graphics("../figures/gazemodel_simulated_u.png")
```

# Study 3: Components of gaze understanding
## Procedure Theory of mind battery

|     |     |     |     |
| --- | --- | --- | --- |
| **Task name** | **Author** | **Description** | **Material used** |
| Diverse Beliefs | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Wellman et al., 1996 | Child sees a toy figure of a girl and a sheet of paper with bushes and a garage drawn on it. “Here’s Linda. Linda wants to find her cat. Her cat might be hiding in the bushes or it might be hiding in the garage. Where do you think the cat is? In the bushes or the garage?” This is the *own-belief* question., If the child chooses the bushes: “Well, that’s a good idea, but Linda thinks her cat is in the garage. She thinks her cat is in the garage.” (or vice versa) Then the child is asked the *target* question: “So where will Linda look for her cat? in the bushes or in the garage?”, To be correct, the child must answer the target question opposite from his/her answer to the *own-belief* question. | Toy figure of girl, Sheet of paper with bushes and a garage (e.g., garden) |
| Knowledge Access | Wellman & Liu, 2004 → Pratt & Bryant (1990), Pillow (1989) | Children see a nondescript plastic box with a drawer containing a small plastic toy dog inside the closed drawer. “Here’s a drawer. What do you think is inside the drawer?” (The child can give any answer she/he likes or indicate that she/he does not know). Next, the drawer is opened and the child is shown the content of the drawer: “Let’s see…it’s really a dog inside!” Close the drawer: “Okay, what is in the drawer?”, Then a toy figure of a girl is produced: “Polly has never ever seen inside this drawer. Now here comes Polly. So, does Polly know what is inside the drawer?” (*target* question) “Did Polly see inside this drawer?” (*memory* question”, To be correct, the child must answer the target question “no” and answer the memory control question “no”. | Toy figure of another girl, Plastic box with drawer, Toy dog |
| Contents False Belief | Wellman & Liu, 2004 → Perner, Leekam, & Wimmer, 1987; see also Wellman et al., 2001 | The child sees a clearly identifiable band-aid box with a plastic toy pig inside the closed band-aid box. ‘‘Here’s a band-aid box. What do you think is inside the band-aid box?’’ Next, the band-aid box is opened: ‘‘Let’s see … it’s really a pig inside!’’ The band-aid box is closed: ‘‘Okay, what is in the band-aid box?’’ Then a toy figure of a boy is produced: ‘‘Peter has never ever seen inside this band-aid box. Now here comes Peter. So, what does Peter think is in the box? Band-Aids or a pig? (the *target* question) ‘‘Did Peter see inside this box?’’ (the *memory* question). To be correct the child must answer the target question ‘‘band-aids’’ and answer the memory question ‘‘no.’’ | Toy figure of a boy, Band-aid box , Toy pig |
| Explicit False Belief | Wellman & Liu, 2004 → Wellman & Bartsch, 1989; Siegal & Beattie, 1991 | Children see a toy figure of a boy and a sheet of paper with a backpack and a closet drawn on it. ‘‘Here’s Scott. Scott wants to find his mittens. His mittens might be in his backpack or they might be in the closet. Really, Scott’s mittens are in his backpack. But Scott thinks his mittens are in the closet.’’ ‘‘So, where will Scott look for his mittens? In his backpack or in the closet?’’ (the *target* question) ‘‘Where are Scott’s mittens really? In his backpack or in the closet?’’ (the _reality_ question). To be correct the child must answer the target question ‘‘closet’’ and answer the reality question ‘‘backpack.’’ | Toy figure of another boy, Sheet of paper with a children’s room with a backpack and a clost on it |
| Perspective-Taking Level 2 | Flavell et al., 1981 | Picture of a turtle is placed horizontally on the table between the child and experimenter, so that it appeared upside down (or right side up) from the child’s side and right side up (or upside down) from the experimenter’s. The child’s task is to indicate in which of these two orientations it appeared to the experimenter (“standing on its feet” or “lying on its back”). | Picture of a turtle |
| Perspective-Taking Level 2 | Flavell et al., 1981 | Children are shown a horizontally placed picture of a worm lying between a red blanket and a blue blanket. The child was then asked if the worm appeared to the experimenter, seated opposite, to be lying on the red blanket or on the blue blanket. | Picture of a worm between two blankets |

@@

### Model comparisons
To identify which (social-)cognitive components were needed to best explain the TANGO score, we compared GLMMs that predicted the mean imprecision in gaze understanding by age + the respective task score: imprecision in non-social vector estimation, the ToM aggregate score, and/ or the aggregate of the two perspective-taking tasks (subset of ToM battery). For example, the model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`). The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results below.

```{r magnet_modelcomparison}
magnet_modelcomparison <- readRDS("../saves/magnet_modelresults.rds") %>%
  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

knitr::kable(magnet_modelcomparison, format = "latex", booktabs = TRUE) %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

@@

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::

```{=tex}
\endgroup
```

>>>>

---
title             : "Supplements for the manuscript  'Variation in gaze following across the life span: A process-level perspective'"
shorttitle        : "Supplements"

author:
  - name          : "Julia Christin Prein"
    affiliation   : "1,2"
  - name          : "Luke Maurits"
    affiliation   : "1"
  - name          : "Annika Werwach"
    affiliation   : "3,4"
  - name          : "Daniel B. M. Haun"
    affiliation   : "1,*"
  - name          : "Manuel Bohn"
    affiliation   : "1,2,*"
affiliation:
  - id            : "1"
    institution   : "Department of Comparative Cultural Psychology, Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany"
  - id            : "2"
    institution   : "Institute of Psychology, Leuphana University Lüneburg, Germany"
  - id            : "3"
    institution   : "Center for Lifespan Psychology, Max Planck Institute for Human Development, Berlin, Germany"
  - id            : "4"
    institution   : "Max Planck School of Cognition, Leipzig, Germany"
  - id            : "*"
    institution   : "Shared senior authorship" 
floatsintext      : yes
bibliography      : ["../../references.bib"]
figurelist        : yes
tablelist         : yes
footnotelist      : no
linenumbers       : yes
mask              : yes
draft             : no
header-includes:
  - \usepackage{setspace}
  - \captionsetup[figure]{font={stretch=1}}
  - \renewcommand{\thefigure}{S\arabic{figure}} \setcounter{figure}{0}
  - \renewcommand{\thetable}{S\arabic{table}} \setcounter{table}{0}
  - |
    \makeatletter
    \renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-1em}%
      {\normalfont\normalsize\bfseries\typesectitle}}

    \renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
      {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
      {-\z@\relax}%
      {\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
    \makeatother

csl               : "`r system.file('rmd', 'apa7.csl', package = 'papaja')`"
documentclass     : "apa7"
output            : papaja::apa6_pdf
editor_options: 
  markdown: 
    wrap: sentence
---

@@

# Study 1: Lifespan
## Participants
For further information on the participants in Study 1, please see Supplementary Table S1.

@@

Originally, we fitted the models on a trial-by-trial basis with the following structure in `R: performance ~ age + symmetricPosition + trialNr + (1 + symmetricPosition + trialNr | subjID)`. However, the Gaussian Process model was computationally heavy. Therefore, we simplified the model structure, aggregated data on a subject level, and included only age as an effect. We then visually compared the model predictions of the original and the simplified models with each other. As you can see in Figure \@ref(fig:S1), results of the two models did not differ notably.

@@

# Study 2: Computational cognitive model 
## Analysis
### Gaze model prediction
Our gaze model predicts that TANGO trials vary in their difficulty, resulting in a U-shaped pattern: Participants' imprecision should increase, the further out the target lands (towards the very left/right sides). Since the task is presented on a screen, there is a natural border towards one side. Imagine the target lands to the very right side. Participants' imprecision cannot click further right because the screen ends; all their uncertainty about the target location faces the inner, left-hand side now. Therefore, the predicted U-shaped pattern should decrease again towards the screen borders. For previous reliability analyses [@prein2023tango], we had increased the trial number for an adult sample (N = 70; each 30 trials). Interestingly, here we found the expected shape in the data: the U-pattern decreased again towards the screen ends (Figure \@ref(fig:S2)).

## Inference parameter estimates per individual
As can be seen in Figure \@ref(fig:S3) and Figure \@ref(fig:S4), the gaze model estimated the inference parameter for each individual. Across individuals, the inference parameter varied in the estimated magnitude and level of uncertainty. In general, estimates for more precise individuals (i.e., smaller inference parameter value) showed decreased levels of uncertainty.

@@

Please note that our random guessing model acts like 100% noise: the predictions of a participant’s click on a trial level range uniformly from 0 to 1920 (the whole screen range). The mean comes down to the center, namely 960. However, as you can see in Figure \@ref(fig:S5)A below, the U shape is weaker compared to the other models. Most importantly, note that this is only the case when you average across all the trials. When you look at the individual trial-by-trial level, the models are defined by different data-generating processes, and therefore, their predictions differ, too (Figure \@ref(fig:S5)C). In our correlational plots (Figure  S\@ref(fig:S5)B), we see that the gaze model is clearly favored. This highlights the benefit that we gain through the modeling approach: even though a certain (U) pattern in the data could be elicited from several different models, we can disentangle which process is most likely causing this pattern.

# Study 3: Components of gaze understanding
## Procedure Theory of mind battery 
For the Theory of Mind battery, we followed the standardized procedure as described below. The battery was administered in German and presented in the order as stated below.

### (1) Diverse Beliefs [@wellman2004scaling]
Material: Girl figure, leaf with garage & bush. 
Experimenter (E): "Look, this is Linda. Linda wants to find her cat. The cat is either hiding behind the bush or in the garage. Where do you think the cat is hiding? Behind the bush or in the garage?" (own-belief question). Child: "Garage". E: "That's a good idea! But Linda thinks her cat is behind the bush. She thinks her cat is behind the bush. So, where will Linda look for her cat? Behind the bush or in the garage?" (target question)

### (2) Knowledge Access [@wellman2004scaling]
Material: Yellow box, pig figure, female figure.
E: "Look, here's a box. What do you think is in the box?" [Child answers] [Box opens] E: "Let's see...oh, there's actually a pig inside!" [Box is closed] E: "What's in the box?" [E pulls out figure] E: "That's Polly. Polly has never looked in the box. So, does Polly know what's in the box? (target question) Has Polly ever looked in the box? (control question)"

### (3) Contents False Belief [@wellman2004scaling]
Material: Smarties box, figure of a dog, figure of a boy. 
E: "Here is a Smartie box. What do you think is inside?" [Smartie box is opened] E: "Let's see...there's actually a dog inside!" [Smartie box is closed] E: "Okay, what's in the Smartie box?" [Man's figure is taken out] E: "This is Peter. Peter has never looked inside the Smartie box. What does Peter think is in the box? Smarties or a dog? (target question) Has Peter ever looked in the box? (memory question)"

### (4) Explicit False Belief [@wellman2004scaling]
Material: Figure of a boy, sheet with cupboard & rucksack on it.
E: "This is Scott. Scott wants to find his gloves. The gloves could be in his backpack or they could be in the closet. In reality, they are in the backpack. But Scott thinks his gloves are in the closet. So, where will Scott look for his gloves? In the backpack or in the closet? (target question) Where are his gloves really? In the backpack or in the closet? (reality question)"

### (5) Perspective-Taking Level 2 version I [@flavell1981development; @flavell1981younga]
Material: Picture of turtle. 
E: "Look, here's a picture of a turtle. I'll put it between us. What does the turtle look like to you, is it standing on its feet or lying on its back? (own perspective question) And what does it look like to me? Does it stand on its feet for me or does it lie on its back? (other perspective question)."

### (6) Perspective-Taking Level 2 version II [@flavell1981development; @flavell1981younga]
Material: Picture of worm between two pillows.
E: "Now we have a worm lying between two pillows. I'll put it between us again. How does it look to you, is the worm lying on the red or the blue cushion? (own perspective question) And what does it look like to me - is the worm lying on the red or the blue cushion? (other perspective question)"

@@

### Model comparisons
To identify which (social-)cognitive components were needed to best explain the TANGO score, we compared GLMMs that predicted the mean imprecision in gaze understanding by age + the respective task score: imprecision in non-social vector estimation, the ToM aggregate score, and/ or the aggregate of the two perspective-taking tasks (subset of ToM battery). For example, the model notation in `R: tango_mean ~ age_centered + magnet_scaled + perspective_scaled`). The model including the non-social vector estimation task (magnet) and the two perspective-taking tasks won, as indicated by the model comparison results shown in Supplementary Table S2.

@@

```{=tex}
\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}
```
::: {#refs custom-style="Bibliography"}
:::
```{=tex}
\endgroup
```

# Supplementary Tables

(ref:tableS1-caption) **Participants in Study 1**. Age is given in years.

```{r tableS1, include = T, out.width = "100%", caption = "(ref:tableS1-caption)"}
lifespan_sample <- readRDS("../saves/lifespan_sample.rds")

knitr::kable(lifespan_table, format = "latex", booktabs = TRUE, caption = "Participants in Study 1. Age is given in years.") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

```{r tableS2, include = T, out.width = "100%", caption = "(ref:tableS2-caption)"}
magnet_modelcomparison <- readRDS("../saves/magnet_modelresults.rds") %>%
  mutate(across(c(WAIC, Weight, ELPD_DIFF, SE_ELPD_DIFF), as.numeric)) %>%
  mutate_if(is.numeric, round, 2)

knitr::kable(magnet_modelcomparison, format = "latex", booktabs = TRUE, caption = "Model comparisons ToM tasks.") %>% 
  kable_styling(latex_options = c("scale_down", "HOLD_position"))
```

# Supplementary Figures

(ref:S1-caption) **Comparison between models on a trial- or subject-level**. Grey dots show data of each trial. Solid lines show the mean predicted developmental trajectory for both models. Line color denotes model structure (yellow: trial-level; black: aggregated on subject-level).

```{r S1, include = T, out.width = "100%", fig.cap = "(ref:S1-caption)"}
knitr::include_graphics(c("../figures/lifespan_plot.png"))
```

(ref:S2-caption) **Gaze funnel for adult sample with higher trial number (30 trials)**. The x-axis shows the target position, binned into 10 sections. The y-axis shows participants' imprecision in target widths.

```{r S2, include = T, out.width = "100%", fig.cap = "(ref:S2-caption)"}
knitr::include_graphics("../figures/gazefunnel_adults.pdf")
```

(ref:S3-caption) **Gaze model estimates faceted by individual**. Density curves show the distribution of the inference parameter by individual.

```{r S3, include = T, out.width = "100%", fig.cap = "(ref:S3-caption)"}
knitr::include_graphics("../figures/supplements_gazemodel_facetedinference.pdf")
```

(ref:S4-caption) **Gaze model estimates ordered by descending inference parameter value**. Density curves show the distribution of the inference parameter across individuals.

```{r S4, include = T, out.width = "100%",fig.cap = "(ref:S4-caption)"}
knitr::include_graphics("../figures/supplements_gazemodel_indinference.pdf")
```

(ref:S5-caption) **Predictions of alternative models across target positions.** A: Predicted U-pattern across target positions by the different models. Note that this is averaged across trials and displays imprecision, i.e., the absolute distance between the target center and the click. B: Correlation between the predicted imprecision and the observed imprecision, by target position and age group. C: Predicted click coordinates (cf. not imprecision) by target position across the different models.

```{r S5, include = T, out.width = "100%",fig.cap = "(ref:S5-caption)"}
knitr::include_graphics("../figures/gazemodel_simulated_u.png")
```
